---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SRS

<!-- badges: start -->
<!-- badges: end -->

The goal of SRS is to to take one or multiple simple random samples (SRS) of the specified size from an assumed population which are elements of a vector with length>1, and return the summary statistics including sample mean, sample standard deviation and etc.

The functions in SRS can additionally be used to illustrate the asymptotic properties of estimates based on SRS, which is also known as the central limit theorem.

## Installation

You can install SRS from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("QianYe-stat/SRS")
```
## Development of SRS
* Initialize the package folder using `create_package("~/Mye.package/SRS")`
* Initialize Git repo using `use_git()`. 
* Use `use_r("is_wholenumber")` and `use_r("SRSampling")` to create 2 separate blank R script files. Copy and paste the codes for the 2 functions from assignment-1b to the 2 R script files respectively.
* Commit changes and run `check()`
* Modify `DESCRIPTION`. Mostly manually but with `use_mit_license("Qian Ye")` to  fill-in the license information.
* Run `use_package("stats")` to add `stats` package to Import field in `DESCRIPTION` as `sd()` function from `stats` is used in my package.
* Update my R codes with `sd` replaced by `stats::sd`.
* Run `check()`, `install()` and then `library(SRS)`. It's working!
* Create `tests` folder using `use_testthat()`
* Create a test file using `use_test("SRSampling")` and write `test_that` functions to test `SRSampling` function.
* Run `test()`. Passed!
* Update R codes with a specially formatted comment begin with `#'`. Run `document()` to generate corresponding `*.Rd` files. Try `?SRSampling`. It's working!
  + note that, I choose not to `@export` for the `is_wholenumber` function. Because it's sourced from `examples` under `integer{base}` and out of the objective of `SRS` package which is to take SRS samples.
* Manually configured a GitHub Personal Access Token (PAT) following the [instructions](https://happygitwithr.com/github-pat.html#github-pat).
* Run `use_github()` to connect the local `SRS` package and Git repository to a companion repository on GitHub.
* Create `README` file by using `use_readme_rmd()`. 
* Manually modify the `README.Rmd` file and run `build_readme()` to render it.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SRS)
## basic example code
###### informal tests #######
pop.1 <- rnorm(1000,0,10)
# take a SRS from x of size=10, show.SRS=TRUE
SRSampling(x=pop.1, size=10, show.SRS=T)

# take 20 SRS from x of size=10, show.SRS=FALSE
SRSampling(x=pop.1, size=10, rep=20)
```


Some expected errors and warnings
```{r, error=TRUE}
## size>length(pop.2)
pop.2 <- rnorm(10,0,10)#
SRSampling(x=pop.2, size=15, rep=20) # error; not run

## non-integer size
SRSampling(x=pop.2, size=5.8) # warning

## x=numeric(0)
SRSampling(x=numeric(0), size=1) # error; not run
```

input with NA
```{r}
## x with NA
pop.3 <- c(1,2,3,4,NA)
SRSampling(x=pop.3, size=5, na.rm=T)
SRSampling(x=pop.3, size=5)

```


