---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SRS

<!-- badges: start -->
<!-- badges: end -->

The goal of SRS is to to take one or multiple simple random samples (SRS) of the specified size from an assumed population which are elements of a vector with length>1, and return the summary statistics including sample mean, sample standard deviation and etc.

The function can additionally be used to illustrate the asymptotic properties of estimates based on SRS, which is also known as the central limit theorem.

## Installation

You can install SRS from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("QianYe-stat/SRS")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SRS)
## basic example code
###### informal tests #######
pop.1 <- rnorm(1000,0,10)
# take a SRS from x of size=10, show.SRS=TRUE
SRSampling(x=pop.1, size=10, show.SRS=T)

# take 20 SRS from x of size=10, show.SRS=FALSE
SRSampling(x=pop.1, size=10, rep=20)
```


Some expected errors and warnings
```{r, error=TRUE}
## size>length(pop.2)
pop.2 <- rnorm(10,0,10)#
SRSampling(x=pop.2, size=15, rep=20) # error; not run

## non-integer size
SRSampling(x=pop.2, size=5.8) # warning

## x=numeric(0)
SRSampling(x=numeric(0), size=1) # error; not run
```

input with NA
```{r}
## x with NA
pop.3 <- c(1,2,3,4,NA)
SRSampling(x=pop.3, size=5, na.rm=T)
SRSampling(x=pop.3, size=5)

```


