---
title: "Use_SRS_to_Show_CLT"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Use_SRS_to_Show_CLT}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## This is an example that how to use `SRSampling` function in SRS package to illustrate the Central Limit Theorem. 

1. Suppose $X$ following a uniform distribution within interval $(0,12)$; that is 
$$X\sim \mathcal{Unif}(0,12).$$
So, $\mathrm{E}(X)=6$ and $\mathrm{Var}(X)=12$.

If we generate a large amount of random numbers following $\mathcal{Unif}(0,12)$ and assume they are the target population of interest.
Let's see the distribution of the target population, as well as the summary statistics. 
```{r}
# generate target population: pop
set.seed(123)
pop <- runif(10000, 0, 12)

# the histogram should be close to the uniform density
hist(pop)

# population mean; should be close to E(X)=6
mean(pop)

# population variance; should be close to Var(X)=12
var(pop)
```

2. Use the `SRS` package to take multiple SRS from the population and study the sampling distribution.

   + Sample size=10; 1000 replicates
```{r setup}
library(SRS)
set.seed(123)
sample.10 <- SRSampling(pop, size=10, rep=1000)

# extract the sample means for every SRS
sample.10.means <- sample.10$sample.mean$values

# the histogram
hist(sample.10.means)

# mean of sample mean
sample.10$sample.mean$mean

# var of sample mean
sample.10$sample.mean$se^2
```
   + Sample size=100; 1000 replicates
```{r}

set.seed(123)
sample.100 <- SRSampling(pop, size=100, rep=1000)

# extract the sample means for every SRS
sample.100.means <- sample.10$sample.mean$values

# the histogram
hist(sample.100.means)

# mean of sample mean
sample.100$sample.mean$mean

# var of sample mean
sample.100$sample.mean$se^2
```
3. By observing the histogram and summary statistics of sample means from SRS, the Central Limit Theorem is confirmed; that is
\[
\bar{X} \sim \mathcal{N}(\mu, \sigma^2)\\
\mu=\mathrm{E}(X), \quad \sigma^2=\frac{\mathrm{Var}(x)}{n},
\]
where n is the sample size.
